---
title: "Business Forecasting HW 3 - Sriven Sikhinam"
output:
  html_document:
    df_print: paged
---
Take the data set from HW3 and perform the Forecasting Methods we went over during class. (Please refer to Lecture_4.Rmd file).

- Business Forecasting HW 3 
dataset: auscafe 

auscafe - this data is a compilation of Monthly expenditures on eating out in Australia. Data is modeled from April 1982 - September 2017 and it is in the scale of Billion Dollar Amt. 

```{r}
library(fpp)
library(fpp2)
library(TTR)
df = auscafe
attributes(df)
```
```{r}
plot(df)
```
```{r}
Acf(df)
```
```{r}
mean_forecast = meanf(df, 5)
plot(mean_forecast)
```
```{r}
naive_forecast = naive(df, 5)
plot(naive_forecast)
```
```{r}
#Random Walk 
rwf_forecast = rwf(df,5)
rwf_forecast = rwf(df,5, drift = TRUE)
```
```{r}
#Seasonal Naive
snaive_forecast = snaive(elecequip,5)
```
```{r}
#Moving Averages 
MA5_forecast = ma(df, order = 5)
MA9_forecast = ma(df, order = 9)
```
```{r}
#plot all in a single chart 
plot(mean_forecast)
lines(naive_forecast$mean, col = "red")
lines(rwf_forecast$mean, col = "green")
lines(snaive_forecast$mean, col = "black")
lines(MA5_forecast, col = "Pink")
lines(MA9_forecast, col = "Blue")
```
```{r}
#what other attributes are there?
attributes(naive_forecast)
```
```{r}
#Decomposition 
ets_forecast = ets(df)
plot(df)
```
```{r}
attributes(ets_forecast)
```
```{r}
ets_forecast$mse
```
```{r}
#HoltWinters 
HW_forecast = HoltWinters(df)
plot(df)
```
```{r}
SSE_Simple = HoltWinters(df, beta = FALSE, gamma = FALSE)
attributes(SSE_Simple)
```
```{r}
plot(SSE_Simple)
```
```{r}
SSE_Simple$SSE
```
```{r}
head(SSE_Simple$fitted)
```
```{r}
forecast_ets_1 = forecast.ets(ets_forecast, h= 5)
plot(forecast_ets_1)
forecast_ets_2 = forecast(ets_forecast, h = 5)
plot(forecast_ets_2)
```


The forecast ets method really gives a good prediction on the time series dataset as it resembles closer to the past behavior of the model. 